\section{Microarchitecture}
\label{sec:arch}

Coarse grain execution exposes energy saving opportunities in most pipeline
stages. In this section we discuss the flow of basicblocks through different
pipeline stages and elaborate on how energy is saved in each stage.

provide an example of the execution here.  it should contain a code with
multiple BB's with local/global registers, header ins.  It should show flow of
BB in a 2-wide machine. provide execution schedule, update and issue register
activity. instruction issue logic information.

Below, we discuss the various architectural components of this architecture.
Figure XX illustrates the processor stages in detail.

Discuss the overall structure of a basicblock. Focus on its unique attributes:
MOV ops for turning global to local, local registers, header instructions. Show
the image of BB.
\input{bb_structure}

Show the hardware support structure for BB. This includes bbWindow and bbROB.
\input{bb_window}

Discuss the overall CPU frontend. Focus on what is differnet.
\input{cpu_frontend}

Discuss the overall CPU backend. Focus on what is differnet.
\input{cpu_backend}

Discuss BB scheduling. Perhaps here the example discussion is a great fit. (but
        cook up the example throughout this whole section and explain it in
        detail here.). This step should signify the dynamic ooo execution
aspect.
\input{scheduling}

Focus on speculation support for memory and branch and how it impacts execution.
again describe the example here.
\input{speculation}


